Stats for the convergence paper

### 2019-12-18 models/paper/convergence_paper_models.Rmd
fig4

ggplot(t4, aes(x = baseline.averages, y = individual.averages, colour = lex_typicality2, shape = lex_typicality2, linetype = lex_typicality2)) +
  guides(size = F) +
  geom_point() +
  geom_smooth(se = F, method = 'loess', formula = 'y ~ x') +
  facet_wrap( ~ type) +
  scale_shape_discrete(name="Lexical\ntypicality") +
  # scale_colour_discrete(name="Lexical\ntypicality") +
  xlab('verb baseline regularization') +
  ylab('verb ESP regularization') +
  scale_colour_brewer(palette = 'Set2', name="Lexical\ntypicality")
# ggsave('interactionplot.pdf', device = cairo_pdf, width = 12.5, height = 4)
ggsave('fig4_2019.pdf', width = 12.5, height = 4)

>>>>

ggplot(t4, aes(x = baseline.averages, y = individual.averages, colour = lex_typicality2, shape = lex_typicality2, linetype = lex_typicality2)) +
  guides(size = F) +
  geom_point() +
  geom_smooth(se = F, method = 'loess', formula = 'y ~ x') +
  facet_wrap( ~ type) +
  scale_shape_discrete(name="Lexical\ntypicality") +
  # scale_colour_discrete(name="Lexical\ntypicality") +
  xlab('verb baseline regularization') +
  ylab('verb ESP regularization') +
  guides(linetype = F) +
  scale_colour_brewer(palette = 'Set2', name="Lexical\ntypicality")
# ggsave('interactionplot.pdf', device = cairo_pdf, width = 12.5, height = 4)
ggsave('fig4_2019.pdf', width = 12.5, height = 4)
